---
title: "104各科相關係數矩陣"
output: html_notebook
---

## 各科變異數
國,英,數甲,數乙,歷,地,公,物,化,生

For each subject, store each student's score in 'each_stud_score', and calculate its variance.
each_subj_var[10]
//移除分數最低0.1%者 
```{r}
df1 = read.csv("../organized data/104 各科之分數分布.csv")

stud_cnt = colSums(df1)  # number of students of each subject

each_subj_var<- vector("double", length = 10)   #variance of each subject
each_subj_mean<- vector("double", length = 10)   #mean of each subject


for( x in 1:10){
    each_stud_score <- vector("double", length = stud_cnt[x])
    chinese = df1[,x]
    grade = 100
    cnt = 1
    for(i in 1:101){
      for(j in 1:chinese[i]){
         if(chinese[i] == 0 )
              next;
         each_stud_score[cnt] = grade
         cnt = cnt+1
      }
      if(grade==100) grade=grade-0.5
      else grade = grade-1
    }
   
     n = cnt-1                                      #真正的總人數 of subject1
    #discount persons
    n = floor(n * 0.999)
    each_subj_var[x] = var(each_stud_score[1:n])*(n-1)/n
    each_subj_mean[x] = sum(each_stud_score[1:n])/n
    #print(each_subj_var[x])
    rm(each_stud_score)   #remove the vector
}
```


## 各組合變異數
移除分數<3者***
再移除分數最低0.5%者 ***
For each group, store each student's score in 'each_stud_score', and calculate its variance.
```{r}
df2 = read.csv("../organized data/104 各組合之分數分布.csv")
grade_array = df2[,2]
num_of_people_array = df2[,3]
each_stud_score <- vector("double", length = 55000)   #temp, score of each student
each_group_var<- vector("double", length = 50)  #variance of each group
each_group_mean<- vector("double", length = 50)     #mean of each group

for(i in 0:49){  #total 50 groups 0-49
  cnt=1
  a =1+i*100
  b=100+i*100
  
  for(j in a:b)
  {
      if(num_of_people_array[j] == 0 )
          next;
      for(xxx in 1:num_of_people_array[j]){
          #each_stud_score[cnt] = grade_array[j]
          #cnt = cnt+1  
          
          #filter out 0 score. 
          if(grade_array[j] > 3) {
            each_stud_score[cnt] = grade_array[j]
            cnt = cnt+1  
          }
      }
  }
 
  n = cnt-1                                      #真正的總人數 of group1
  #discount persons
  n = floor(n * 0.995)
  each_group_var[i+1] = var(each_stud_score[1:n])*(n-1)/n    #variance of group1
  each_group_mean[i+1] = sum(each_stud_score[1:n])/(n) 
  #cat(n," ",each_group_var[i+1],"\n")      #print 各組合人數&變異數
}
```

## 科目組合矩陣[n,45]
```{r}
df3 = read.csv("../organized data/104 各組合之採計科目.csv")

sigma_index = c("12","13","14","15","16","17","18","19","110","23","24","25","26","27","28","29","210","34","35","36","37","38","39","310","45","46","47","48","49","410","56","57","58","59","510","67","68","69","610","78","79","710","89","810","910")

# 科目組合矩陣 x:各組合所包含的變異數(權重=1)  y:共50組合
mtrx <- matrix(0,nrow=50,ncol=45)  
colnames(mtrx) = sigma_index

#兩科目在同一組合中之次數
inSameGroup <- matrix(nrow = 10, ncol = 10) 
colnames(inSameGroup) = c('國','英','數甲','數乙','歷','地','公','物','化','生')
rownames(inSameGroup)= c('國','英','數甲','數乙','歷','地','公','物','化','生')
for(i in 1:9)
  for(j in (i+1):10)
     inSameGroup[i,j] = 0

#sum of subjects' variance in each group
var123plus <- vector("double", length = 50)   #sum of subjects' var in each group


get_sigma_index <- function(a,b)
{
   str=paste(as.character(a),as.character(b),sep="")
   x <- which(sigma_index == str)
   return (x)
} 


for(i in 1:50){   #60
  for(j in 2:df3[i,1]){  #2
    for(k in (j+1):(df3[i,1]+1)){  #3,4
        mtrx[i, get_sigma_index(df3[i,j],df3[i,k]) ] = sqrt(each_subj_var[df3[i,j]]*each_subj_var[df3[i,k]])  #correlation coefficient
        inSameGroup[df3[i,j],df3[i,k]]=inSameGroup[df3[i,j],df3[i,k]] + 1
    }
    var123plus[i] = var123plus[i] + each_subj_var[ df3[i,j] ]
  }
  var123plus[i]= var123plus[i] + each_subj_var[ df3[i,j+1] ]
}

#inSameGroup

y1 <- vector("double", length = 50) 
for(i in 1:50){
   y1[i] = each_group_var[i] - var123plus[i]
   y1[i]= y1[i]/2
   #print(y1[i])
}

mtrx_orig = mtrx
```


#OLS: 預測相關係數矩陣
y1[60] =  mtrx[60,45] %*% [45,1]

Remove rare rows and columns
columns '49' '410' and associated rows
```{r}
ind2 = mtrx_orig[, '49'] == 0
ind3 = mtrx_orig[, '410'] == 0
rowind = ind2 & ind3
y2 = y1[rowind]

mtrx2 = data.frame(mtrx_orig[rowind,])
mtrx2 = mtrx2[,which(colSums(abs(mtrx2))!=0)]  #remove column if the whole column are all 0
mtrx2 = mtrx2[,!colnames(mtrx2) %in% 'X49']    #remove column 'X49' since only one group contains both subject4 & subject9
mtrx2 = mtrx2[,!colnames(mtrx2) %in% 'X410']

summary( lm(y2~.,data = mtrx2) )
```

no intercept
```{r}
summary( lm(y2~.-1,data = mtrx2) )
```

##國,英,數甲,物,化,生
remove  combinations of 4, 5, 6, 7
this includes, X45, X46, X47, X56, X57, X67

```{r}
mtrx_orig2 = data.frame(mtrx_orig)
cind1 = colnames(mtrx_orig2) %in% c('X24', 'X25', 'X26', 'X27', 'X45', 'X46', 'X47', 'X56', 'X57', 'X67')
tmp1 = mtrx_orig2[,cind1]
tmp2 = rowSums(tmp1)
#keep only if row sums are zero
rowind3 = tmp2 == 0
mtrx_orig2a = mtrx_orig2[rowind3,!cind1]
#keep only if column sums are not zero
tmp3 = colSums(mtrx_orig2a)
mtrx_orig2a = mtrx_orig2a[, tmp3 != 0]
y3 = y1[rowind3]

summary( lm(y3~.,data = mtrx_orig2a) )
```